Clinical Trial Data Analysis

### 2017-02-05 results/results.Rmd
Minor changes to results Rmd

@@

If the null hypothesis is true, then $\varepsilon = Y - \beta_0 - \beta_1X$.
Therefore, we may estimate the errors $\hat{\varepsilon}$ by $Y - \hat{Y}$, where $\hat{Y}$ is obtained by regressing $Y$ on $X$ but not $Z$.
The $\varepsilon$ are orthogonal to $X$ and $Z$.
Assuming that the $\hat{\varepsilon}$ are ``close'' to $\varepsilon$, thenthese estimated $\hat{\varepsilon}$ are approximately exchangeable within sites.

>>>>

The permutation tests rely on the `permuter` R package.  If you haven't installed it, you should run the following command:

```{r download_permuter, eval = FALSE}
devtools::install_github("statlab/permuter")
```

@@

If the null hypothesis is true, then $\varepsilon = Y - \beta_0 - \beta_1X$.
Therefore, we may estimate the errors $\hat{\varepsilon}$ by $Y - \hat{Y}$, where $\hat{Y}$ is obtained by regressing $Y$ on $X$ but not $Z$.
Assuming that the $\hat{\varepsilon}$ are ``close'' to $\varepsilon$, then these estimated $\hat{\varepsilon}$ are approximately exchangeable within sites.
